Towards a Mechanized Proof of Noninterference

### 2013-12-18 paper/paper.tex
Finally figured out how to format operational semantics rules...
Operational semantics written.
Fixes to semantics and proof of first 2 lemmas.

\documentclass[a4paper]{article}
\usepackage{mathpartir}
\usepackage{amssymb}
\usepackage{amsthm}
%\usepackage{float}
%\floatstyle{boxed}
%\restylefloat{figure}

@@

@@

\begin{lemma}[Soundness]
  \label{lem:soundness}
  Let $i \in \{1, 2\}$. If $e \to e'$, then $\lift{e}_i \to \lift{e'}_i$.
\end{lemma}
\begin{proof}
  TODO
\end{proof}

\begin{lemma}
  \label{lem:stuck_bracket}
  If $e$ is stuck, then $\lift{e}_i$is stuck for some $i \in \{1, 2\}$.
\end{lemma}
\begin{proof}
  TODO
\end{proof}

\begin{lemma}[Completeness]
  \label{lem:stuck_bracket}
  If $e$ is stuck, then $\lift{e}_i$is stuck for some $i \in \{1, 2\}$.
\end{lemma}
\begin{proof}
  TODO
\end{proof}

@@

\section{Mechanizing Proofs}

>>>>

\documentclass[a4paper]{article}
\usepackage{mathpartir}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
%\usepackage{float}
%\floatstyle{boxed}
%\restylefloat{figure}

@@

\begin{figure}
  Basic reductions
  \begin{align}
    (\textsf{fix} f . \lambda x . e) v
    \textsf{ } \to \textsf{ } &
    e[x \Leftarrow v][f \Leftarrow \textsf{fix} f . \lambda x . e]
    \tag{$\beta$}
    \label{eq:beta}
    \\
    \textsf{if } 1 \textsf{ } e_1 \textsf { } e_2
    \textsf{ } \to \textsf{ } &
    e_1
    \tag{if-true}
    \label{eq:if-true}
    \\
    \textsf{if } (k \neq 1) \textsf { } e_1 \textsf { } e_2
    \textsf{ } \to \textsf{ } &
    e_2
    \tag{if-false}
    \label{eq:if-false}
    \\
    \textsf{let }  x := v \textsf{ in } e
    \textsf{ } \to \textsf{ } &
    e[x \Leftarrow v]
    \tag{let}
    \label{eq:let}
  \end{align}

  Lifting
  \begin{align}
    < v_1 | v_2 > v
    \textsf{ } \to \textsf{ } &
    < v_1 \lift{v}_1 | v_2 \lift{v}_2 >
    \tag{lift-app}
    \label{eq:lift-app}
    \\
    \textsf{if } < v_1 | v_2 > \textsf{ } e_1 \textsf{ } e_2
    \textsf{ } \to \textsf{ } &
    < \textsf{if } v_1 \textsf{ } \lift{e_1}_1 \textsf{ } \lift{e_2}_1 |
    \textsf{ if } v_2 \textsf{ } \lift{e_1}_2 \textsf{ } \lift{e_2}_2 >
    \tag{lift-if}
    \label{eq:lift-if}
    \\
    &
    \infer*
    {
    e_1 \to e_1' \\
    }
    {
    <e_1 | e_2> \textsf{ } \to \textsf{ } <e_1' | e_2>
    }
    \tag{bracket-left}
    \label{eq:bracket-left}
    \\
    &
    \infer*
    {
    e_2 \to e_2' \\
    }
    {
    <e_1 | e_2> \textsf{ } \to \textsf{ } <e_1 | e_2'>
    }
    \tag{bracket-right}
    \label{eq:bracket-right}
  \end{align}
  \caption{Operational semantics for \langName.}
  \label{fig:operational_semantics}
\end{figure}

@@

\begin{lemma}[Soundness]
  \label{lem:soundness}
  Let $i \in \{1, 2\}$. If $e \to e'$, then $\lift{e}_i \to^*
  \lift{e'}_i$.\footnote{Notice that this is not the same statement as the
  Soundness lemma in Simonet and Pottier's paper~\cite{InfoFlowML}, which does
  not give a variable number of steps for the conclusion.  We will discuss this
  change in Section~\ref{sec:mechanizing}.}
\end{lemma}
\begin{proof}
  This can be seen by examining each of the operational semantics rules in
  Figure~\ref{fig:operational_semantics}.
\end{proof}

\begin{lemma}
  \label{lem:stuck_bracket}
  If $e$ is stuck, then $\lift{e}_i$is stuck for some $i \in \{1, 2\}$.
\end{lemma}
\begin{proof}
  By induction on the structure of $e$.

  \begin{case}[$e = v$]
    In this case, $e$ is not stuck.
  \end{case}

  \begin{case}[$e = v_1 v_2$]
    If $e$ is stuck and is an application, this means that neither
    \ref{eq:beta} nor \ref{eq:lift-app} applies.  This means that $v_1$ can
    neither be a fixpoint function or some bracketed value.  As a result,
    $\lift{v_1}_i$ can not be a fixpoint function, and so it is stuck.
  \end{case}

  \begin{case}[$e = \textsf{ if } v \textsf{ } e_1 \textsf{ } e_2$ or $e =
    \textsf{ let } x := v \textsf{ in } e$]
    These are similar to the previous case.  The value $v$ can not be an integer
    and so the lifted version of $v$ can not be an integer, meaning the lifted
    expression is also stuck.
  \end{case}

  \begin{case}[$e = < e_1 | e_2 >$]
    Since $e$ is stuck, then by \ref{eq:bracket-left} and \ref{eq:bracket-right}
    we know that both $e_1$ and $e_2$ must be stuck.  Since $e$ is not a final
    value, we know either $e_1$ or $e_2$ must not be a final value and, as a
    result, stuck.
  \end{case}
\end{proof}

\begin{lemma}[Completeness]
  \label{lem:completeness}
  Assume $\lift{e}_i \to^* a_i$ for all $i \in \{1, 2\}$.  Then, there exists a
  final value $a$ such that $e \to^* a$.
\end{lemma}
\begin{proof}
  TODO
\end{proof}

@@

\section{Mechanizing Proofs}
\label{sec:mechanizing}
